Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-03-10 Milestone_1/01-chap1.Rmd
fix diagram

The remainder of the report is organised as follows. Chapter \ref{se:research-problem} outlines the three research problems. Chapter \ref{se:overview} gives an overview of the thesis including descriptions of three projects. Chapter \ref{#se:project-1} presents the human subject experiments conducted in the first project along with the prototype of the automatic visual inference system. Chapter \ref{se:project-2}

@@

# Overview of the Thesis {se:overview}

>>>>

The remainder of the report is organised as follows. Chapter \ref{se:research-problem} outlines the three research problems. Chapter \ref{se:overview} gives an overview of the thesis including descriptions of three projects. Chapter \ref{se:project-1} presents the human subject experiments conducted in the first project along with the prototype of the automatic visual inference system. Chapter \ref{se:project-2}

@@

# Overview of the Thesis {#se:overview}
